Lineage Analysis of CRISPR and shRNA Screens

### 2018-08-24 lineages_18Q3.Rmd

knitr::kable(crispr_signif[1:100, c(1, 5, 6, 7, 8, 10)], caption = "CRISPR Screen: Wilcoxon Test Results Comparing Mutant and Wildtype Cell Lines (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
```

@@

knitr::kable(shrna_signif[1:100, c(1, 5, 6, 7, 8, 10)], caption = "shRNA Screen: Wilcoxon Test Results Comparing Mutant and Wildtype Cell Lines (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
```

@@

>>>>

knitr::kable(filter(crispr_signif, p < 0.1)[, c(1, 5, 6, 7, 8, 10)], caption = "CRISPR Screen: Wilcoxon Test Results Comparing Mutant and Wildtype Cell Lines (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
```

@@

knitr::kable(filter(shrna_signif, p < 0.1), c(1, 5, 6, 7, 8, 10)], caption = "shRNA Screen: Wilcoxon Test Results Comparing Mutant and Wildtype Cell Lines (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
```

@@

```{r fig.height=12, fig.width=12}
makeCRISPRgrob("KRAS")
```

```{r fig.height=12, fig.width=12}
makeCRISPRgrob("TP53")
```
